\documentclass[article]{scrartcl}    % classe article di KOMA
%\usepackage[total={8.5in,10.75in}, top=1.2in, left=0.9in, right=0.9in, includefoot]{geometry}
\reversemarginpar
\newcommand{\MarginDate}[1]{\marginpar{\raggedleft\itshape\small#1}}
\usepackage[LabelsAligned]{currvita}	% un buon pacchetto per CV
\usepackage[nochapters]{classicthesis} % stile ClassicThesis
\usepackage{url}	% per gli indirizzi Internet
\usepackage{verbatim}
\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}}
\renewcommand{\cvlistheadingfont}{\large}
\renewcommand{\cvlabelfont}{\qquad}
%Setup hyperref package, and colours for links, text and headings
\usepackage{hyperref}		
\hypersetup{	colorlinks,breaklinks,
			urlcolor=Maroon, 
			linkcolor=Maroon}
\newlength{\datebox}\settowidth{\datebox}{August 2009 - May 2010}

\newcommand{\NewWorkExperience}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\textit{#1}}\hspace{1.5em} #2 #3
\vspace{0.5em}}

\areaset[15mm]{360pt}{750pt}
\setlength{\marginparwidth}{7em}

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize}

\newcommand{\Sep}{\vspace{2em}}

\begin{document}
\thispagestyle{empty}

\begin{cv}{  \spacedallcaps{Mantas A. Vidutis} }
\vspace{1.5em}

\spacedlowsmallcaps{Personal Data}
\vspace{0.5em}

% Top line of personal data, used to be a birthday
% \NewWorkExperience{}{\textit{Chicago,}}{13 November 1920}

\NewWorkExperience{email}{\href{mailto:mantas@vidutis.com}{mantas@vidutis.com}}{}

\NewWorkExperience{phone}{+1 301 300 6122}{}
\vspace{1.5em}

\noindent\spacedlowsmallcaps{Work Experience}
\vspace{0.5em}

\NewWorkExperience{May 2010 - Current}{Backstop Solutions Group, Chicago}{}

\Description{\MarginDate{Accounting \& CRM}Enterprise Java development on BSG’s main Accounting/CRM platform, as well as original development on scalable services to sync email from Exchange 2007/2010 servers. Following an Agile (Scrum) development model with a two week development iteration. Technologies used include Thrift and Hibernate. Testing tools include FitNesse, JUnit and Squish.}

\Sep

\NewWorkExperience{August 2009 - May 2010}{N. Illinois Hockey League, Chicago}{}

\Description{\MarginDate{Statistics \& Tournament Scheduling}A dynamic user, schedule and statistics management system written in Python using Django, SQLite and PostgreSQL. My personal contributions included the game scheduling algorithm and the statistics page filtering.}

\vspace{1.5em}

\spacedlowsmallcaps{Open Source Contributions}
\vspace{0.5em}

\NewWorkExperience{2010}{Mahout, Apache}{}

\Description{\MarginDate{Machine Learning \& Data Mining}Designed and implemented a decision tree learning and classifying tool that runs on top of Hadoop. The concept was inspired by the Google PLANET paper on distributed decision trees. Mahout is a machine learning framework written in Java. }

\vspace{1.5em}

\spacedlowsmallcaps{Languages}
\vspace{0.5em}

\newlength{\techbox}
\settowidth{\techbox}{Objective C}
\Description{\parbox{\techbox}{\textsc{Java}}\ \ $\cdotp$\ \  \ \parbox{\techbox}{\textsc{Python}}}
\MarginDate{Advanced}
\vspace{0.5em}

\Description{\parbox{\techbox}{\textsc{Clojure}}\ \ $\cdotp$\ \  \ \parbox{\techbox}{\textsc{Haskell}}\ \ $\cdotp$\ \  \ \parbox{\techbox}{\textsc{Objective C}}\ \ $\cdotp$\ \  \ \parbox{\techbox}{\textsc{JavaScript}}} 
\MarginDate{Intermediate}

\vspace{1.5em}

\spacedlowsmallcaps{Education}
\vspace{0.5em}

\NewWorkExperience{May 2011}{Illinois Institute of Technology, Chicago}{}

\Description{Major: Computer Science\ \ $\cdotp$\ \  Advisor: Prof.~Mattox \textsc{Beckman}\MarginDate{Bachelor of Science}}

\begin{comment}
\Sep

\NewWorkExperience{July 2006}{Bocconi University,}{Milan}

\Description{Major: Computer Science\ \ $\cdotp$\ \  \MarginDate{Some Other Education}\newline Thesis: ``Sublinear and Locally Sublinear Prices'' \newline Advisor: Prof.~Mattox \textsc{Beckman}\ \ $\cdotp$\ \  Gpa: 28.61/30}

\end{comment}

\vspace{1.5em}

\spacedlowsmallcaps{Honors}
\vspace{0.5em}

\Description{Camras Heald Scholarship \ \ $\cdotp$\ \ IIT University Scholarship }
\MarginDate{Scholarships}

\vspace{0.5em}

\Description{IIT Dean's List \ \ $\cdotp$\ \ IPRO Presentation First Place (Fall 2009)}
\MarginDate{Awards}

\vspace{0.5em}

\Description{ACM IIT President \ \ $\cdotp$ \ \ Local Area Network Club President}
\MarginDate{Leadership}

\vspace{1.5em}

\spacedlowsmallcaps{Additional Information}
\vspace{0.5em}

\newlength{\langbox}
\settowidth{\langbox}{American English}
\Description{\parbox{\langbox}{\textsc{American English}}\ \ $\cdotp$\ \  \ Fluent}
\MarginDate{Spoken Languages}
\vspace{0.5em}

\Description{\parbox{\langbox}{\textsc{Lithuanian}}\ \ $\cdotp$\ \  \ Fluent}
\vspace{0.5em}
\Description{\parbox{\langbox}{\textsc{French}}\ \ $\cdotp$\ \  \ Elementary}

\vspace{1em}

\Description{Aikido\ \ $\cdotp$\ \ Typography\ \ $\cdotp$\ \  Photography\MarginDate{Personal Interests}}
\enlargethispage{\baselineskip}
\end{cv}
\end{document}