\documentclass[article]{scrartcl}    % classe article di KOMA
%\usepackage[total={8.5in,10.75in}, top=1.2in, left=0.9in, right=0.9in, includefoot]{geometry}
\reversemarginpar
\newcommand{\MarginDate}[1]{\marginpar{\raggedleft\itshape\small#1}}
\usepackage[LabelsAligned]{currvita}    % un buon pacchetto per CV
\usepackage[nochapters]{classicthesis} % stile ClassicThesis
\usepackage{url}	% per gli indirizzi Internet
\usepackage{verbatim}
\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}}
\renewcommand{\cvlistheadingfont}{\large}
\renewcommand{\cvlabelfont}{\qquad}
%Setup hyperref package, and colours for links, text and headings
\usepackage{hyperref}		
\hypersetup{	colorlinks,breaklinks,
			urlcolor=Maroon, 
			linkcolor=Maroon}
\newlength{\datebox}\settowidth{\datebox}{August 2009 - May 2010}

\newcommand{\NewWorkExperience}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\textit{#1}}\hspace{1.5em} #2 #3
\vspace{0.5em}}

\areaset[15mm]{360pt}{750pt}
\setlength{\marginparwidth}{7em}

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize}

\newcommand{\Sep}{\vspace{2em}}

\begin{document}
\thispagestyle{empty}

\begin{cv}{  \spacedallcaps{Mantas A. Vidutis} }
\vspace{1.5em}

\spacedlowsmallcaps{Personal Data}
\vspace{0.5em}

% Top line of personal data, used to be a birthday
% \NewWorkExperience{}{\textit{Chicago,}}{13 November 1920}

\NewWorkExperience{email}{\href{mailto:mantas@vidutis.com}{mantas@vidutis.com}}{}

\NewWorkExperience{phone}{+1 4155 MANTAS}{}
\vspace{1.5em}

\noindent\spacedlowsmallcaps{Work Experience}
\vspace{0.5em}

\NewWorkExperience{Sept 2011 - April 2013}{Getaround, San Francisco}{}

\Description{\MarginDate{Transportation \& Collaborative Consumption}Backend Software Engineer responsible for the majority of the implementation and logic behind car rentals, payments and SMS notifications. System was built on Google App Engine using Python 2.7. Datastore/memcached for persistence. Employee \#19. }

\Sep

\NewWorkExperience{May 2011 - August 2011}{Wakemate, San Francisco}{}

\Description{\MarginDate{Consumer Health \& Wellness}Sole backend developer of the Wakelytics analytics platform and the Wakestore in-house e-commerce platform. Wrote and managed the API used by the mobile applications to retrieve and upload sleep data. Managed the storing and architecture of user sleep data. Implemented UI modifications. Work was in Python/Django with a PostgreSQL/memcached backend and JQuery/JS/Compass UI tools.}

\Sep

\NewWorkExperience{May 2010 - May 2011}{Backstop Solutions Group, Chicago}{}

\Description{\MarginDate{Accounting \& CRM}Enterprise Java development on BSG’s main Accounting/CRM platform, as well as original development on scalable services to sync email from Exchange 2007/2010 servers. Following an Agile (Scrum) development model with a two week development iteration. Technologies used include Thrift, Hibernate, Struts and Stripes. Testing tools include FitNesse, JUnit and Squish.}

%\Sep

%\NewWorkExperience{August 2009 - May 2010}{N. Illinois Hockey League, Chicago}{}

%\Description{\MarginDate{Statistics \& Tournament Scheduling}A dynamic user, schedule and statistics management system written in Python using Django, JQuery and PostgreSQL. Personal contributions included the game scheduling algorithm and the statistics page filtering.}

\vspace{1.5em}

\spacedlowsmallcaps{Personal Projects}
\vspace{0.5em}

\NewWorkExperience{2010}{After Credits, Foursquare}{}

\Description{\MarginDate{Social Networking \& Context Awareness}Designed, implemented and deployed a foursquare \href{https://foursquare.com/app/after-credits/TOW5VTUUKO44O2PUNK04VQLLREF4BZKINYGAYOT1VPB3HTUE}{app} to notify a user if there was a scene after the credits of a movie they were checked in to. Featured on the Foursquare Engineering \href{http://engineering.foursquare.com/2012/08/16/checking-in-at-the-movies-heres-how-to-never-miss-an-after-the-credits-teaser-again/}{blog}, \href{http://aboutfoursquare.com/are-there-any-clips-after-the-credits-new-connected-app-tells-you/}{aboutfoursquare.com} and the Foursquare \href{https://foursquare.com/apps/}{App Gallery}. Written in Clojure, Redis/memcached persistence, deployed on Heroku. Over 9 thousand users.}

\vspace{1.5em}

\spacedlowsmallcaps{Languages}
\vspace{0.5em}

\newlength{\techbox}
\settowidth{\techbox}{Javascript}
\Description{\parbox{\techbox}{\textsc{Python}}\ \ $\cdotp$\ \  \ \parbox{\techbox}{\textsc{Clojure}}\ \ $\cdotp$\ \  \ \parbox{\techbox}{\textsc{Java}}}
\MarginDate{Advanced}
\vspace{0.5em}

\Description{\parbox{\techbox}{\textsc{Haskell}}\ \ $\cdotp$\ \  \ \parbox{\techbox}{\textsc{JavaScript}}} 
\MarginDate{Intermediate}

\vspace{1.5em}

\spacedlowsmallcaps{Education}
\vspace{0.5em}

\NewWorkExperience{May 2011}{Illinois Institute of Technology, Chicago}{}

\Description{Major: Computer Science\ \ $\cdotp$\ \  Focus: Data Mining \& Machine Learning}
\Description{Minor: Psychology\MarginDate{Bachelor of Science} \ \ $\cdotp$\ \  Advisor: Prof.~Mattox \textsc{Beckman}}

\vspace{1.5em}

\spacedlowsmallcaps{Honors}
\vspace{0.5em}

\Description{Camras Heald Scholarship \ \ $\cdotp$\ \ IIT University Scholarship }
\MarginDate{Scholarships}

\vspace{0.5em}

\Description{IIT Dean's List \ \ $\cdotp$\ \ IPRO Presentation First Place (Fall 2009)}
\MarginDate{Awards}

\vspace{0.5em}

\Description{ACM IIT President \ \ $\cdotp$ \ \ Local Area Network Club President}
\MarginDate{Leadership}

\vspace{1.5em}

\spacedlowsmallcaps{Additional Information}
\vspace{0.5em}

\newlength{\langbox}
\settowidth{\langbox}{American English}
\Description{\parbox{\langbox}{\textsc{American English}}\ \ $\cdotp$\ \  \ Fluent}
\MarginDate{Spoken Languages}
\vspace{0.5em}

\Description{\parbox{\langbox}{\textsc{Lithuanian}}\ \ $\cdotp$\ \  \ Fluent}
\vspace{0.5em}
\Description{\parbox{\langbox}{\textsc{French}}\ \ $\cdotp$\ \  \ Elementary}

\vspace{1em}

\Description{Aikido\ \ $\cdotp$\ \ Typography\ \ $\cdotp$\ \  Photography\MarginDate{Personal Interests}}
\enlargethispage{\baselineskip}
\end{cv}
\end{document}